Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-20 WSSSPE3/report/wg_main_industry_interaction.tex
tried converting text to better paragraph form

\textbf{Goal}

\emph{What is the goal of doing research on transition pathways?}

Can we identify collaborations that have occurred and try to understand which were successful, which were unsuccessful, and what factors contributed to these successes/failures?

Can we determine what each partner wants to get out of such a collaboration?
For example, why would industry be interested in collaborating with academia? 
Or why would academia be interested in collaborating with industry?

How could we design a study that focused on the impact of the software in
undergoing this type of transition?

\textbf{Potential outcomes}

A set of case studies that look at successful and unsuccessful
transitions of researchers between academia and industry. This might address 
each of the transition types (described below). Successful transitions are
described as those that lead to either weak or strong sustainability (also
defined below).

Create a generalizable framework that might allow for the study of different
transition pathways (other than academia to industry).

\textbf{General Definitions}

We characterize transitions in the following ways:
\begin{itemize}

>>>>

First, we discussed the \textbf{goals} of this research, attempting to answer the 
question \emph{What is the goal of doing research on transition pathways?}
A number of research questions arose:  Can we identify collaborations that have 
occurred and try to understand which were successful, which were unsuccessful, 
and what factors contributed to these successes/failures? Can we determine what 
each partner wants to get out of such a collaboration? For example, why would 
industry be interested in collaborating with academia? Or why would academia 
be interested in collaborating with industry? How could we design a study that 
focused on the impact of the software in undergoing this type of transition?

Next, we imagined \textbf{potential outcomes} of research on this topic, involving 
a set of case studies that look at successful and unsuccessful
transitions of researchers between academia and industry. This might address 
each of the transition types (described below). Successful transitions are
described as those that lead to either weak or strong sustainability (also
defined below). In addition, the results from this research might help create a 
generalizable framework that might allow for the study of different transition 
pathways (other than academia to industry).

Finally, we created some \textbf{general definitions} for these concepts; we 
characterize transitions in the following ways:
\begin{itemize}
